Class Project Report: Boundary-free Technology Mapping using Gr\"obner Basis

### 2015-05-01 techwriting/ASPDAC/appendix_fmcad.tex
all write-up from virtue machine

\subsection{Design a Normal Basis Multiplier using $\lambda$-Matrix}
Imitating the structure of SMPO, just specify the gates' connections for the first clock cycle, then following cycles are
automatically completed by cyclic shifting operands $A$ and $B$. The whole design procedure is based on a $n \times n$ $k$-th $\lambda$-Matrix.

@@

>>>>

\subsection{Design Angew's SMPO using $\lambda$-Matrix}
Imitating the structure of SMPO, just specify the gates' connections for the first clock cycle, then following cycles are
automatically completed by cyclic shifting operands $A$ and $B$. The whole design procedure is based on a $n \times n$ $k$-th $\lambda$-Matrix.

@@

\subsection{Theory about RH-multiplier}
\label{sec:RHmulti}
Assume there are 3 word variables from $\mathbb F_{2^k}$: $A = (a_0,a_1,\dots,a_{k-1}), B = (b_0,b_1,\dots,b_{k-1})$
and $C = (c_0,c_1,\dots,c_{k-1})$, they have relation $C = A\cdot B$. Define function
$$F_i(A,B) = a_{i-g}b_{i-g}\beta +\sum_{j=1}^{v}z_{i,j}\delta_j, 0\leq i\leq k-1$$
where $v = \lfloor \frac{k}{2}\rfloor, \delta_j = \beta^{1+2^j}, 1\leq j\leq v$, $\beta$ is normal element.
$g$ is a binary variable which determines value of $z_{i,j}$ as follows:

(i) $k$ is odd, for $1\leq j < \lceil \frac{k}{2} \rceil$
\begin{displaymath}
z_{i,j} = \left\{
\begin{array}{ll}
(a_i+a_{i+j})(b_i+b_{i+j}) & g=0\\
a_ib_{i+j} + a_{i+j}b_i & g=1
\end{array}\right.
\end{displaymath}

(2) $k$ is even, for $1\leq j < \lceil \frac{k}{2} \rceil$
\begin{displaymath}
z_{i,j} = \left\{
\begin{array}{ll}
b_i(a_i+a_{i+v}) & g=0\\
a_ib_{i+v} & g=1
\end{array}\right.
\end{displaymath}

Here $i+j$ and $i+v$ stands for $i+j \pmod k$ and $i+v\pmod k$. With the definition, we can
introduce a theorem which serves as basic concept of RH-multiplier:
\begin{Theorem}
$$C = (((F_{k-1}^2 + F_{k-2})^2 + F_{k-3})^2 + \cdots + F_1)^2 + F_0$$
where $F_i\in \mathbb F_{2^k}$ is a short form of $F_i(A,B)$ defined above.
\end{Theorem}
Proof omitted.

In this paper we choose $g=1$ to build AESMPO. The definition of function $F$ shows exactly
the way to construct a RH-multiplier, note multiplication in $\mathbb F_2$ is equivalent to
AND gate in Boolean logic circuits, and addition is equivalent to XOR gate, respectively.

### 2015-05-01 techwriting/ASPDAC/oldtheory.tex
all write-up from virtue machine

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./sequential_fig.eps}
\end{center}
\caption{A typical sequential circuit block view}
\label{fig:sequential}
\end{figure}

A transition function $\Delta$ is a Boolean function about state outputs and all inputs, i.e.
\begin{displaymath}
t_i = \Delta_i(x, s_0, s_1, \dots, s_{k-1})
\end{displaymath}
This constrain could also be written in the form of equation $polynomial = 0$:
\begin{displaymath}
t_i - \Delta_i(x, s_0, s_1, \dots, s_{k-1}) = 0
\end{displaymath}
Solution to this equation is limited within $\{0, 1\}$, which is set of all elements in Galois field $\mathbb{F}_2$.
Furthermore, there exists a one-to-one corresponding relation from Boolean space to Galois field on higher dimension: 
$\mathbb{B}^k \to \mathbb{F}_{2^k}$, which means it is possible to find a set of elements in $\mathbb{F}_{2^k}$ representing
all Boolean values every bit of a bit vector can take. In Galois field, a as \ref{table:booltogalois} shows.
\begin{table}[h]
\centering
\begin{tabular}{|c|c||c|c|} 
\hline
$a_3a_2a_1a_0$ & Polynomial     &$a_3a_2a_1a_0$ & Polynomial  \\
\hline
$0000$        & $0$           & $1000$  &$\alpha^3$\\
\hline
$0001$        & $1$           & $1001$  & $\alpha^3 + 1$\\
\hline
$0010$        &  $\alpha$       & $1010$ & $\alpha^3 + \alpha$  \\
\hline
$0011$        &  $\alpha + 1$   & $1011$ &  $\alpha^3+\alpha+1$\\
\hline
$0100$        &  $\alpha^2$     &  $1100$ &  $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^2 + 1$ & $1101$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        &  $\alpha^2 + \alpha$ & $1110$ &  $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        & $\alpha^2+\alpha+1$ & $1111$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  ${\mathbb{F}}_{2^4} = {\mathbb{F}}_2[x]
\pmod{x^4+x^3+1}$}\label{table:booltogalois}  
\end{table}
A word-level representation on state inputs/outputs can be attained through above correspondence. If the set of 
state inputs $\{s_0, s_1, \dots, s_{k-1}\}$ is denoted by $S$ taking values from $\mathbb{F}_{2^k}$, and
set of outputs $\{t_0, t_1, \dots, t_{k-1}\}$ is denoted by $T$, a word-level transition function can be written as
\begin{displaymath}
T - \Delta(x, S) = 0
\end{displaymath}
If $T - \Delta(x, S)$ is taken as a polynomial $f$, then $f \in \mathbb{F}_{2^k}[x]\ mod\ P(\alpha)$.
\subsection{Gr\"obner Basis Theory}
Gr\"obner basis is used to calculate desired results out of a set of polynomials.
If there exists multiple polynomials $\{f_1, f_2, \dots, f_r\}$ representing constrains on $T, x$ and $S$,
then all polynomials should simultaneously equal to $0$.
\begin{displaymath}
\left\{
  \begin{array}{lc}
  f_1 & = 0\\
  f_2 & = 0\\
  \dots & \ \\
  f_r & = 0
  \end{array} \right.
\end{displaymath}
Solution to these equations is set of values of $(T, x, S)$, which is called \textbf{Variety} of \textbf{ideal}
$I = \langle f_1, f_2, \dots, f_r\rangle $.

@@

\begin{Example}
\label{ex:nb_multi}
Normal basis multiplication: There are 2 binary vectors representing operands of multiplication in normal
basis: $$A = (a_0, a_1, \dots, a_{n-1}),\ B = (b_0, b_1, \dots, b_{n-1})$$ 
the product is also written in normal basis representation: $$C = A*B = (c_0, c_1, \dots, c_{n-1})$$
Describe calculation procedure for the most significant digit of product with a function: 
$$c_{n-1} = f(a_0, a_1, \dots, a_{n-1}; b_0, b_1, \dots, b_{n-1})$$
Square both side: $C^2 = A^2*B^2$, i.e. the second significant digit 
$$c_{n-2} = f(a_{n-1}, a_0, a_1, \dots, a_{n-2}; b_{n-1}, b_0, b_1, \dots, b_{n-2})$$ 
By this method it is easy to get all digits of product $C$.
\end{Example}

@@

\begin{figure}[hbt]
\begin{center}
\includegraphics[scale=0.3]{./stg_fig.ps}
\end{center}
\caption{State transition graph of sample FSM}
\label{fig:stg}
\end{figure}

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./fsm_fig.eps}
\end{center}
\caption{Gate-level circuit of combinational logic block of sample FSM}
\label{fig:fsm}
\end{figure}

@@

One important technique to check sequential equivalence is \textbf{state space traversal}. In this example,
Breath-First-Search (BFS) is employed for traversal, which can be described with following algorithm:

@@

Transition equations here contains some Boolean operators, they can be re-written in terms of operations in Galois fields. 
In $\mathbb{F}_{2}$, let $TRUE = 1, FALSE = 0$, for either element $a$ in this field, considering $0 + 0 = 1 + 1 \equiv 0\ (mod\ 2)$
and $0 + 1 = 1 + 0 \equiv 1\ (mod\ 2)$, the inverse of $a$ is: $\overline{a} = 1 + a$. Similarly all Boolean operators
can be converted within $\mathbb{F}_{2}$, table \ref{table:booltogalois_op} gives part of them and their corresponding
operations in $\mathbb{F}_{2}$:
Also note that there is no specification on initial primary input $x$, in Gr\"obner basis approach this means $x$ is smoothed by
reversely using Shannon's expansion.
\begin{table}
\centering
\begin{tabular}{|c|c|} \hline
Boolean operator & operation in $\mathbb{F}_{2}$\\ \hline
$\overline{a}$ & $1 + a$\\ \hline
$a\ and\ b$ & $ab$\\ \hline
$a\ or\ b$ & $a + b + ab$\\ \hline
$a \oplus b$ & $a + b$\\
\hline\end{tabular}
\caption{Some Boolean operators and corresponding operations in $\mathbb{F}_{2}$}
\label{table:booltogalois_op}
\end{table}
Using elimination term order: $intermediate\ bit$-$level\ signals\ >\ bit$-$level\ primary\ inputs/outputs\ >\ S\ >\ T$, compute Gr\"obner basis for ideal
$J = \langle f_1, f_2, \dots, f_{12}\rangle $, the result will include one polynomial $f_T$ contains only variable $T$. In this example,
$f_T = T^2+(\alpha+1)T+\alpha$. This polynomial equals to $T^2-(\alpha+1)T+\alpha$ since coefficients of polynomial representation in $\mathbb{F}_{2^2}$ are
limited within $\mathbb{F}_{2}$, where $x \equiv -x\ (mod\ 2)$ for any element $x$ in the field. Solution to $f_T = 0$ is $T = 1\ or \ T = \alpha$, which shows that next
state the machine just reached is $\{S_1(01), S_2(10)\}$.

@@

\begin{figure*}[tb]
\begin{center}
\includegraphics[width=\textwidth]{./mySMPO.eps}
\end{center}
\caption{5-bit SMPO}
\label{fig:SMPO}
\end{figure*}

@@

  $from^0 = reached = \F(S)$\;
  \Repeat{$new^i == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB w/ elimination term order$<I_{ckt}, from^{i-1}>$\;
	$new^i \gets $generator of $<to^i> + (<T^4-T>:<reached>)$\;
  	$reached \gets $generator of $<reached> \cdot <new^i>$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm}\label{alg:modified}
\end{algorithm}

@@

\section{Functional Verification}
\subsection{Sequential Galois Arithmetic Multiplier}
Our experiment is to verify the function of a Galois field multiplier after certain clock cycles.
The following design is Sequential Multiplier with Parallel Output (SMPO),
a Normal Basis multiplier based on Massey-Omura algorithm. Inputs and outputs
are all 5-bit word taking value from ${\mathbb F}_{2^5}$. After loading operands
 A and B, setting all output latches to 0 and running for 5 iterations, the 
output should be $R = A\cdot B$ (mod $x^5 + x^2 + 1$).

Similarly, build elimination ideal for all gates/operations and induce
initial states of latches. However, instead of eliminating all variables
to one, this example adopts abstraction term order
and keeps the polynomial contains function between output and inputs.
Here the lex ordering is $\{all\ bit$-$level\ variables\} > R > \{A, B\}$, and objective
polynomial is $R + \mathcal{F}(A, B)$.

@@

For 5-bit normal basis multiplication, the $i$-th digit of product can be written as
\begin{align}
R_i &= b_ia_{i+1} + b_{i+1}(a_i + a_{i+3}) + b_{i+2}(a_{i+3} + a_{i+4}) \nonumber\\
&+ b_{i+3}(a_{i+1} + a_{i+2}) + b_{i+4}
(a_{i+2} + a_{i+4}),\ 0\leq i\leq 4 \nonumber
\end{align}
It is possible to calculate every conjunctive term in the product simultaneously within one clock cycle,
on distinct bits. 
Use cyclic similarity of above function, following executions are operated: 
\begin{Example}
Sequential Multiplier Protocol:
\begin{itemize}
\item \textbf{Initial}\ \ $R_0 = R_1 = R_2 = R_3 = R_4 = 0$
\item \textbf{Clock 1}\ \ $R_0 = a_1b_0, R_1 = b_2(a_1 + a_4), R_2 = b_4(a_0 + a_1), R_3 = b_1(a_4 + a_0), 
			R_4 = b_3(a_1 + a_3)$
\item \textbf{Clock 2}\ \ $R_0 = b_3(a_1 + a_3) + a_0b_4, R_1 = a_1b_0 + b_1(a_0 + a_3), R_2 = b_2(a_1 + a_4)
			+ b_3(a_4 + a_0), R_3 = b_4(a_0 + a_1) + b_0(a_3 + a_4), R_4 = b_1(a_4 + a_0) + b_2(a_0 + a_2)$
\item \textbf{$\dots$}
\item \textbf{Clock 5}\ \ $R_0 = c_0, R_1 = c_1, R_2 = c_2, R_3 = c_3, R_4 = c_4$, i.e. $R = A\cdot B$.
\end{itemize}
\end{Example}

>>>>

\begin{figure}[tb]
\begin{center}
\includegraphics[width=3.5in]{./sequential_fig.eps}

\end{center}
\caption{A typical sequential circuit block view}
\label{fig:sequential}
\end{figure}

A transition function $\Delta$ is a Boolean function about state outputs and all inputs, i.e.
\begin{displaymath}
t_i = \Delta_i(x, s_0, s_1, \dots, s_{k-1})
\end{displaymath}
This constrain could also be written in the form of equation $polynomial = 0$:
\begin{displaymath}
t_i - \Delta_i(x, s_0, s_1, \dots, s_{k-1}) = 0
\end{displaymath}
Solution to this equation is limited within $\{0, 1\}$, which is set of all elements in Galois field $\mathbb{F}_2$.
Furthermore, there exists a one-to-one corresponding relation from Boolean space to Galois field on higher dimension: 
$\mathbb{B}^k \to \mathbb{F}_{2^k}$, which means it is possible to find a set of elements in $\mathbb{F}_{2^k}$ representing
all Boolean values every bit of a bit vector can take. In Galois field, an example is in table \ref{table:booltogalois}.
\begin{table}[tb]
\centering
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  ${\mathbb{F}}_{2^4} = {\mathbb{F}}_2[x]
\pmod{x^4+x^3+1}$}
\begin{tabular}{|c|c||c|c|} 
\hline
$a_3a_2a_1a_0$ & Polynomial     &$a_3a_2a_1a_0$ & Polynomial  \\
\hline
$0000$        & $0$           & $1000$  &$\alpha^3$\\
\hline
$0001$        & $1$           & $1001$  & $\alpha^3 + 1$\\
\hline
$0010$        &  $\alpha$       & $1010$ & $\alpha^3 + \alpha$  \\
\hline
$0011$        &  $\alpha + 1$   & $1011$ &  $\alpha^3+\alpha+1$\\
\hline
$0100$        &  $\alpha^2$     &  $1100$ &  $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^2 + 1$ & $1101$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        &  $\alpha^2 + \alpha$ & $1110$ &  $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        & $\alpha^2+\alpha+1$ & $1111$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\label{table:booltogalois}  
\end{table}
A word-level representation on state inputs/outputs can be attained through above correspondence. If the set of 
state inputs $\{s_0, s_1, \dots, s_{k-1}\}$ is denoted by $S$ taking values from $\mathbb{F}_{2^k}$, and
set of outputs $\{t_0, t_1, \dots, t_{k-1}\}$ is denoted by $T$, a word-level transition function can be written as
\begin{displaymath}
T - \Delta(x, S) = 0
\end{displaymath}
If $T - \Delta(x, S)$ is taken as a polynomial $f$, then $f \in \mathbb{F}_{2^k}[x]\ mod\ P(\alpha)$.
\subsection{Gr\"obner Basis Theory}
Gr\"obner basis is used to calculate desired results out of a set of polynomials.
If there exists multiple polynomials $\{f_1, f_2, \dots, f_r\}$ representing constrains on $T, x$ and $S$,
then all polynomials should simultaneously equal to $0$.
\begin{displaymath}
\left\{
  \begin{array}{lc}
  f_1 & = 0\\
  f_2 & = 0\\
  \dots & \ \\
  f_r & = 0
  \end{array} \right.
\end{displaymath}
Solution to these equations is set of values of $(T, x, S)$, which is called \textbf{Variety} of \textbf{ideal}
$I = \langle f_1, f_2, \dots, f_r\rangle $.

@@

\begin{Example}
\label{ex:onb_multi}
Normal basis multiplication: There are 2 binary vectors representing operands of multiplication in normal
basis: $$A = (a_0, a_1, \dots, a_{n-1}),\ B = (b_0, b_1, \dots, b_{n-1})$$ 
the product is also written in normal basis representation: $$C = A\cdot B = (c_0, c_1, \dots, c_{n-1})$$
Describe calculation procedure for the most significant digit of product with a function: 
$$c_{n-1} = f(a_0, a_1, \dots, a_{n-1}; b_0, b_1, \dots, b_{n-1})$$
Square both side: $C^2 = A^2\cdot B^2$, i.e. the second significant digit 
$$c_{n-2} = f(a_{n-1}, a_0, a_1, \dots, a_{n-2}; b_{n-1}, b_0, b_1, \dots, b_{n-2})$$ 
By this method it is easy to get all digits of product $C$.
\end{Example}

@@

\begin{figure}[hbt]
\begin{center}
\includegraphics[scale=0.3]{./stg_fig.eps}

\end{center}
\caption{State transition graph of sample FSM}
\label{fig:stg}
\end{figure}

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./fsm_fig.eps}

\end{center}
\caption{Gate-level circuit of combinational logic block of sample FSM}
\label{fig:fsm}
\end{figure}

@@

One important technique to check sequential equivalence is \textbf{state space traversal}. In this example,
Breath-First-Search (BFS) is employed for traversal, which can be described with following algorithm\cite{KallaPartialScan}:

@@

Transition equations here contains some Boolean operators, they can be re-written in terms of operations in Galois fields. 
In $\mathbb{F}_{2}$, let $TRUE = 1, FALSE = 0$, for either element $a$ in this field, considering $0 + 0 = 1 + 1 \equiv 0\ (mod\ 2)$
and $0 + 1 = 1 + 0 \equiv 1\ (mod\ 2)$, the inverse of $a$ is: $\overline{a} = 1 + a$. Similarly all Boolean operators
can be converted within $\mathbb{F}_{2}$, table \ref{table:booltogalois_op} gives part of them and their corresponding
operations in $\mathbb{F}_{2}$:
Also note that there is no specification on initial primary input $x$, in Gr\"obner basis approach this means $x$ is smoothed by
reversely using Shannon's expansion.
\begin{table}[tb]
\centering
\caption{Some Boolean operators and corresponding operations in $\mathbb{F}_{2}$}
\begin{tabular}{|c|c|} \hline
Boolean operator & operation in $\mathbb{F}_{2}$\\ \hline
$\overline{a}$ & $1 + a$\\ \hline
$a\ and\ b$ & $ab$\\ \hline
$a\ or\ b$ & $a + b + ab$\\ \hline
$a \oplus b$ & $a + b$\\
\hline\end{tabular}
\label{table:booltogalois_op}
\end{table}
Using elimination term order: $intermediate\ bit$-$level\ signals\ >\ bit$-$level\ primary\ inputs/outputs\ >\ S\ >\ T$, compute Gr\"obner basis for ideal
$J = \langle f_1, f_2, \dots, f_{12}\rangle $, the result will include one polynomial $f_T$ contains only variable $T$. In this example,
$f_T = T^2+(\alpha+1)T+\alpha$. This polynomial equals to $T^2-(\alpha+1)T+\alpha$ since coefficients of polynomial representation in $\mathbb{F}_{2^2}$ are
limited within $\mathbb{F}_{2}$, where $x \equiv -x\ (mod\ 2)$ for any element $x$ in the field. Solution to $f_T = 0$ is $T = 1\ or \ T = \alpha$, which shows that next
state the machine just reached is $\{S_1(01), S_2(10)\}$.

@@

\begin{figure*}[tb]
\begin{center}
\includegraphics[width=\textwidth]{mySMPO.eps}

\end{center}
\caption{5-bit SMPO. Index $i$ satisfies $0<i<4$, indices $u,v$ are determined by column \# of nonzero entries in $i$-th row of $\lambda$-Matrix $M^{(0)}$, i.e. if entry $M_{ij}^{(0)}$ is a nonzero entry, $u$ or $v$ equals to $i+j \pmod 5$. Index $w = 2i\pmod 5$}
\label{fig:SMPO}
\end{figure*}

@@

  $from^0 = reached = \F(S)$\;
  \Repeat{$new^i == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB w/ elimination term order$\langle I_{ckt}, from^{i-1}\rangle$\;
	$new^i \gets $generator of $\langle to^i\rangle + (\langle T^4-T\rangle:\langle reached\rangle)$\;
  	$reached \gets $generator of $\langle reached\rangle \cdot \langle new^i\rangle$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm}\label{alg:modified}
\end{algorithm}

@@

\section{Functional Verification}
\subsection{Sequential Galois Arithmetic Multiplier}
Our experiment is to verify the function of a sequential Galois field multiplier, which will
give the result of multiplication after certain clock cycles.
Design shown in Fig.\ref{fig:SMPO} is Sequential Multiplier with Parallel Output (SMPO) proposed by 
G.B. Angew et al.\cite{agnew1991implementation},
a Normal Basis multiplier based on Massey-Omura algorithm. Inputs and outputs
are all 5-bit words taking values from ${\mathbb F}_{2^5}$. After loading operands
 $A$ and $B$, setting all output latches to 0 and running for 5 iterations, the 
output should be $R = A\cdot B$ (mod $x^5 + x^2 + 1$).

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./RH.eps}

\end{center}
\caption{5-bit RH-multiplier (AESMPO)}
\label{fig:RHmulti}
\end{figure}

There is another type of SMPO known as RH-multiplier proposed by A. Reyhani-Masoleh and M.A. Hasan
\cite{RHmulti}. Fig.\ref{fig:RHmulti} is the structure of 5-bit RH-multiplier (AND efficient SMPO, or AESMPO).
Theory and design methodology about RH-multiplier is discussed in appendix \ref{sec:RHmulti}.

To apply our approach to verify the function of above SMPO, first is to build elimination ideal for 
all gates/operations and induce initial states of latches. Then, instead of eliminating all variables
to one, we adopt abstraction term order and deduce abstraction polynomial describing the function 
between output and inputs.
Here the lexicographic order is $\{all\ bit$-$level\ variables\} > R > \{A, B\}$, and objective
polynomial is $R + \mathcal{F}(A, B)$.

@@

For 5-bit normal basis multiplication, the $i$-th digit of product can be written as
\begin{align}
c_i &= b_ia_{i+1} + b_{i+1}(a_i + a_{i+3}) + b_{i+2}(a_{i+3} + a_{i+4}) \nonumber\\
&+ b_{i+3}(a_{i+1} + a_{i+2}) + b_{i+4}
(a_{i+2} + a_{i+4}),\ 0\leq i\leq 4 \nonumber
\end{align}
based on results from Example \ref{ex:onbmulti}.

It is possible to calculate every conjunctive term in the product simultaneously within one clock cycle,
on distinct bits. 
Use cyclic similarity of above function, following executions are operated: 
\begin{Example}
Angew's SMPO Protocol: Initial value of all outputs are 0s. After the first clock cycle, the $i$-th
term of equation about $c_i$ is computed. In next clock cycle, output $R_i$ becomes state input $r_i$, which
is used to compute $R_{i+1}: R_{i+1} = r_i + (a_u,a_v)b_w$. In this way, $R_i$ has one more term each clock cycle,
at last after 5 clock cycles it has 5 terms, and equals to the equation about $R_i$.
\begin{itemize}
\item \textbf{Initial}\ \ $R_0 = R_1 = R_2 = R_3 = R_4 = 0$
\item \textbf{Clock 1}\ \ $R_0 = a_1b_0, R_1 = b_2(a_1 + a_4), R_2 = b_4(a_0 + a_1), R_3 = b_1(a_4 + a_0), 
			R_4 = b_3(a_1 + a_3)$
\item \textbf{Clock 2}\ \ $R_0 = b_3(a_1 + a_3) + a_0b_4, R_1 = a_1b_0 + b_1(a_0 + a_3), R_2 = b_2(a_1 + a_4)
			+ b_3(a_4 + a_0), R_3 = b_4(a_0 + a_1) + b_0(a_3 + a_4), R_4 = b_1(a_4 + a_0) + b_2(a_0 + a_2)$
\item \textbf{$\dots$}
\item \textbf{Clock 5}\ \ $R_0 = c_0, R_1 = c_1, R_2 = c_2, R_3 = c_3, R_4 = c_4$, i.e. $R = A\cdot B$.
\end{itemize}
\end{Example}
